Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-06-25 manuscript/supporting_info.tex
Recreated Fig. 1 with proportions in the SI

>>>>

    Within networks, using the proportion of shared interaction partners rather than a tuple resulted in significant relationships between phylogenetic distance and overlap in interaction partners in five herbivory networks and seven pollination networks (compare to seven and 34 networks, respectively, in the main text). In each case, the proportion of shared interaction partners decreased with increasing phylogenetic distance. Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends. The best-fit models for individual networks show much less variation when framing the response as a proportion (Fig.~\ref{lineplot}).

    \begin{figure}[!h]
        \begin{center}
          \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/proportion_regression_lines_full_color.eps}}
        \end{center}
         \caption{\small When considering niche overlap as the proportion of shared interaction partners rather than both the number of interaction partners that are shared and not shared, there is much less variability between networks. The overall trends observed are also much weaker than those detected when using all of the available information. Compare with Fig. 1, main text.
         }
        \label{within_family_regression}
      \end{figure}
